Open-Set Domain Adaptation through Self-Supervision

### 2022-02-04 paper/main.tex
Updated bibliography

\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
Politecnico di Torino\\
Italy\\
{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

>>>>

\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
Politecnico di Torino\\
Italy\\
{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it <- Riordinare}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include\cite{GeoTran}\cite{CenterLoss}\cite{BucciROS}\cite{OldROS}\cite{CarlucciJigsaw} non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
